---
title: "Rworksheet_de la Cruz-Hanz #3b"
<<<<<<< HEAD
output: pdf_document
=======
output:
  pdf_document: default
  html_document:
    df_print: paged
>>>>>>> 6da536dd172a66be9a3c3b6fca2387bc60519f52
date: "2023-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r infodataframe}
personalInfo <- data.frame (
<<<<<<< HEAD
  Respoondents = 1:20,
  Sex = c(1,rep(2,10),1,rep(2,7),1,2))
perosnalInfo

```

=======
  Respondents = 1:20,
  Sex = c(2,2,1,rep(2,7),1,rep(2,7),1,2),
  Fathers_Occupation = c(1,rep(3,3),1:3,rep(1,3),(3:1),3,3,1,3,1,2,1),
  Persons_at_Home = c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6),
  Siblings_at_School = c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2),
  Types_of_Houses = c(1:3,1,1,3,3,1:3,2,3,2,2,rep(3,5),2)
  )
  
  personalInfo
```
```{r summary}
summary(personalInfo)
str(personalInfo)
#It shows the mean, the median the 1st and 3rd Quarter, the minimum and maximum number.
#It also shows the data or observations inside the columns, the column names and how many observations, 
# and variables inside the data frame
 
```

```{r mean of the siblings}
meanSiblings <- mean(personalInfo$Siblings_at_School)
meanSiblings 
#the means of the siblings attending school is not 5 but 2.95 or 3
```
```{r extracting 1st two rows and columns}
firstTwoRowsCols <- personalInfo[1:2,1:2]
firstTwoRowsCols
```
```{r extracting rows 2 and 4, and columns 2 and 4}
rowsColsBetween <- personalInfo[c(3,5),c(2,4)]
rowsColsBetween

```

``` {r house types}
types_house <- personalInfo$Types_of_Houses
types_house
```

```{r select Male and farmer}
maleAndFarmers <- personalInfo[personalInfo$Sex == 1 & personalInfo$Fathers_Occupation == 1, ]
maleAndFarmers
```

```{r female and greater than or equal to 5 members in school}
femaleAndSchool <- personalInfo[personalInfo$Sex == 2 & personalInfo$Siblings_at_School >= 5,]
femaleAndSchool
```

```{r data frame}
df = data.frame(
  Ints=integer(),
  Doubles=double(), Characters=character(),
  Logicals=logical(),
  Factors=factor(),
  stringsAsFactors=FALSE)

print("Structure of the empty dataframe:")
print(str(df))
#the results show many variables or columns are in the data frame, shows the observations, 
#shows the column names and shows the equivalent function for each vector.
```



```{r Household Data}
houseHoldData <- data.frame (
  Respondents = 1:10,
  Sex = c("Male","Female","Female","Male","Male","Female","Female","Male","Female","Male"),
  
  Fathers_Occupation = c(1,2,3,3,1,2,2,3,1,3),
  Persons_at_Home = c(5,7,3,8,6,4,4,2,11,6),
  Siblings_at_School = c(2,3,0,5,2,3,1,2,6,2),
  Types_of_Houses = c("Wood","Congrete","Congrete","Wood","Semi-Congrete","Semi-Congrete","Wood",
                      "Semi-Congrete","Semi-Congrete","Congrete")
)
houseHoldData

```


```{r CSV FILE}
householdCSV <- "household_data.csv"
write.csv(houseHoldData, file = householdCSV, row.names = FALSE)
householdCSV

```

```{r convert sex using factor and change into ingteger}
houseHoldData$Sex <- factor(houseHoldData$Sex, c("Male","Female"),
                     levels(houseHoldData$Sex) <- c(1, 2))

houseHoldData

```

```{r convert types of houses}
houseHoldData$Types_of_Houses <- factor(houseHoldData$Types_of_Houses,
                                        levels = c("Wood", "Congrete", "Semi-Congrete"))


levels(houseHoldData$Types_of_Houses) <- c(1, 2, 3)
houseHoldData 
```
```{r fathers occupation}
fathersOccupation <- houseHoldData$Fathers_Occupation <- factor(houseHoldData$Fathers_Occupation,
                                           levels = c(1, 2, 3),
                                           labels = c("Farmer", "Driver", "Others"))
houseHoldData
```
```{r female and occupation drivers}
femaleAndDrivers <- houseHoldData[houseHoldData$Sex == 2 & 
                                    houseHoldData$Fathers_Occupation == "Driver", ]
femaleAndDrivers
```
```{r 5 or more siblings}
fiveOrMoreSiblings <- houseHoldData[houseHoldData$Siblings_at_School >= 5, ]
fiveOrMoreSiblings
```

```{r interpret graph}
#NUMBER 4 Interpret the graph
#The graph consistently Shows that the negative sentiments are the greatest in number, 
# the neutral being the least and the positive sentiments in the middle. The greatest 
# value of negative sentiments was recorded on July 15, 2020, the Positive sentiments 
# maxing out in July 21, 2020, and the neutral on July 15, 2020 also. All of the 
# sentiments' least number were all recorded on July 20, 2020
```
>>>>>>> 6da536dd172a66be9a3c3b6fca2387bc60519f52
